Hydras \& Co.

### 2022-12-21 doc/chapter-fol.tex
more examples
re-structuring prro scripts in folLogic2
documentation on FOL (draft)

\subsection{Contexts as lists}

@@

\subsection{Proof of Pierce's law}

@@

>>>>

\subsection{Contexts as lists}
\begin{todo}
Describe the \texttt{Prf} type (from \texttt{folProof.v}).

Give examples in a toy language.

Give an example which motivates \texttt{SysPrf}:

$P,P , P\arrow P \arrow Q, \vdash Q$ ?
\end{todo}

@@

\subsection{Proof of Peirce's law}

@@

\index{ackermann}{Exercises}
\begin{exercise}
Prove, using the rules described in 
 \href{../theories/html/hydras.Ackermann.folLogic.html}{Ackermann.folLogic}, the famous \emph{drinkers theorem}:

$$\exists\,x,\; (D(x)\Longrightarrow \forall\,y,\; D(y))$$
\end{exercise}

where $D$ (for ``drinks'') is some predicate symbol of arity $1$.

### 2022-12-21 doc/hydras.tex
documentation on FOL (draft)

\emph{\color{red!80}This maintenance job has just started, and will probably be long to complete. Help is welcome!}

>>>>

\emph{\color{red!80}These maintenance and documentation 
jobs have just started, and will probably be long to complete. Help is welcome!}

\section{File contents}

All Russel O'Connor's files have been stored in two directories, in order to simplify packages maintenance.

\begin{itemize}
\item \texttt{theories/goedel/}: Proofs which depend on 
\texttt{CoqPrime} package.
\item  \texttt{theories/ordinals/Ackermann/} : all the rest:
 definition of primitive recursive functions, first-order  logic,
Peano Arithmetics, G\"{o}del's encoding.
\item Some additions we made: examples, exercices, new notations, etc.,  are stored in a specific directory \texttt{theories/ordinal/MoreAck/}.
\end{itemize}

\section{Warning}
Russel O'Connors contribution contains more than 42 KLoc.
Since its construction, \coq{},  its libraries and recommended style have evolved a lot. We have just started to ``modernize'' this code. We apologize for provisional inconsistencies of presentation (code and documentation).
